Reproducibility in Plant Pathology

### 2021-06-14 README.rmd
Update Docker instructions
Fix grammar in README

```
docker pull adamhsparks/reproducibility_in_plant_pathology
docker run -d -p 8787:8787
```

@@

The file structure follows a normal R package with one exception.
The top-level "/analysis" directory contains the directories and files necessary to reknit the MS Word document of the paper from an Rmd file, "/analysis/paper/paper.Rmd".

A script, `knit_paper.R` is located in `analysis/paper/knit_paper.R` that will knit the Word document

>>>>

```bash
docker pull adamhsparks/reproducibility_in_plant_pathology
docker run -d -p 8787:8787 adamhsparks/reproducibility_in_plant_pathology
```

@@

The file structure follows a normal R package with one exception.
The top-level "/analysis" directory contains the directories and files necessary to re-knit the MS Word document of the paper from an Rmd file, "/analysis/paper/paper.Rmd".

A script, `knit_paper.R`, is located in `analysis/paper/knit_paper.R` that will knit the Word document.
